Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
line break 4th idea of pf

\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$. Then, $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.

@@

\item[(c)] Let $\tau = \max(1,
	\max_{1 \leq i \leq m}(\deg(x_i)))$. Then, $R_\halfcan$ is generated over $R_\halfcan'$
	in degrees up to $\beta$ with $I$ generated over $I'$ in
	degrees up to $\max(2 \beta, \beta + \tau).$
\end{enumerate}
\end{lem}

\sssec*{Idea of proof:} The proof will be fairly involved. To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each best lower approximation. We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and show that the set of elements we produce forms a basis.

Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction} so we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}. The first two hypotheses follow immediately from the definition of block order. Checking the third condition is quite technical but follows from certain slope conditions derived from the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.

>>>>

\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$. Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.

@@

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
	in degrees at most $\beta$ with $I$ generated over $I'$ in
	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
	\max_{1 \leq i \leq m}(\deg(x_i)))$).
\end{enumerate}
\end{lem}

\sssec*{Idea of proof:} The proof will be fairly involved. To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each positive best lower approximation of $\frac{\alpha}{\beta}$. We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and show that the set of elements we produce forms a basis.

Next, part (b) immediately follows from the conclusion of Lemma ~\ref{lem:relations_from_generators_induction}, reducing the proof to verifying the hypotheses of that lemma. 
The first two hypotheses follow immediately from the definition of block order. Checking the third condition is quite technical, but the conditions follow from certain slope conditions, given by ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.
